---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/dis-organization/rgdalwinhdf4?branch=master&svg=true)](https://ci.appveyor.com/project/dis-organization/rgdalwinhdf4)
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rgdalwinhdf4

The goal of rgdalwinhdf4 is to read HDF4 on Windows, using Appveyor.  It works on both 32-bit and 64-bit, 
relying on Rtools being available, and the [rforge/rgdal](https://github.com/rforge/rgdal.git) clone source with the [rwinlibs/gdal2](https://github.com/rwinlib/gdal2.git) (>= 2.2.3) tooling. 


## Installation

Until rgdal is on CRAN with version (> 1.2-16) you will need devtools and 
the Rtools set up on Windows. 

(Untested, see this repo appveyor set up for ). 

```R
devtools::install_github("rforge/rgdal/pkg")
devtools::install_github("dis-organization/rgdalwinhdf4")
```
There's a nice HDF4 sea ice data set for testing with. 

```{r}
## install.packages(c("viridis", "raster", "maptools"))
library(rgdalwinhdf4)
x <- read_hdf4()
## system.file("extdata/asi-AMSR2-s6250-20171211-v5.hdf", package = "rgdalwinhdf4")
library(raster)
r <- flip(raster(x), "y")
extent(r) <- extent(-3950000, 3950000, -3950000, 4350000)
projection(r) <- "+proj=stere +lat_0=-90 +lat_ts=-70 +lon_0=0 +k=1 +x_0=0 +y_0=0 +a=6378273 +b=6356889.449 +units=m +no_defs"
plot(r, col = viridis::viridis(100))
data("wrld_simpl", package = "maptools")
plot(sp::spTransform(wrld_simpl, projection(r)), add = TRUE)
print(r)
```
